---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

<!-- README.md is generated from README.Rmd. Please edit that file -->

# OpenMCE : The TinyMCE Rich Text Editor for Shiny

<!-- badges: start -->

<!-- badges: end -->

Looking to add a Rich Text editing field to your Shiny app? 
Look no further than TinyMCE, as they indicate on their site:

> TinyMCE gives you total control over your rich text editing.

## Deployment Details
This package can use the [Tiny Cloud](https://www.tiny.cloud/) if you have a subscription and set up the `TINYMCE_KEY` *.Renviron* variable (see `?tinymce_key` for setup instructions). If you don't have a subscription, TinyMCE v6.3.0 open source is bundled with this package and will be used in the absence of an API key. The bundled dependencies will include a small Upgrade button on the top right of the editor.

## Installation

``` r
require("remotes")
remotes::install_github("yogat3ch/OpenMCE")
```

### Setting up an API Key (Optional)

Register at [tiny.cloud](https://www.tiny.cloud/) and on your [dashboard](https://www.tiny.cloud/my-account/dashboard/) you'll find the Tiny API Key. The API key is a trial version with \~80 free loads of the editor. You can authorize domains with which you wish to use the key by clicking `Add domain`. See the [setup guide](https://www.tiny.cloud/blog/how-to-get-tinymce-cloud-up-in-less-than-5-minutes/) for more details.

## Examples

```{r, results='hide', echo=FALSE}
examples <- c(
  paste0(c("options", "simple"), sep = "-", "example"),
  "editor_update",
  "editor_text"
)
code_examples <- lapply(rlang::set_names(examples),  \(x) {
  txt <- readLines(system.file(package = "OpenMCE", "examples", paste0(x, "-v1.R")))
  paste0(
    "```r\n",
    paste0(txt, collapse = "\n"),
  "\n```"
  )
})
```

### A Minimal Example

This example uses the TinyMCE editor with basic features.

```{r echo=FALSE, results='asis'}
cat(code_examples$`simple-example`)
```

### A Feature-rich Editor Example

This example highlights some of the many features of the TinyMCE editor.

```{r echo=FALSE, results='asis'}
cat(code_examples$`options-example`)
```

### How to use `editor_update`

This example demonstrates how to use the `editor_update` function for dynamic updating of the editor from the server.

```{r echo=FALSE, results='asis'}
cat(code_examples$`editor_update`)
```

### How to use `editor_text`

This example demonstrates how to manually retrieve the rich text entered in the editor as character encoded HTML

```{r echo=FALSE, results='asis'}
cat(code_examples$`editor_text`)
```

<hr>
This package was inspired by ShinyEditor [deepanshu88/ShinyEditor](https://github.com/deepanshu88/ShinyEditor)
